### 2013-09-17 Docs/visualization/visualization.tex
add some details about using Amrvis

>>>>

\amrvis\ is a tool developed together with \boxlib\ to visualize datasets
from codes built around the \boxlib\ library.  You can download the
\amrvis\ source from: \\
\url{https://ccse.lbl.gov/Downloads/downloadAmrvis.html} \\

\amrvis\ exists in the C++ \boxlib\ framework, so the build system is
slightly different.  A different executable is needed for 2- vs.\ 3-d
datasets.  Edit the {\tt GNUmakefile} and set the compilers (probably
{\tt g++} and {\tt gfortran}) and the dimensionality, and turn off any
of the volume rendering options.  You will need to have the Motif library
installed on your system (or a replacement, such as {\tt lesstif}.

Once the code is built, you visualize a dataset as:
\begin{verbatim}
amrvis3d.Linux.g++.gfortran.ex pltfile
\end{verbatim}
where {\tt pltfile} is the name of the plotfile directory.  Different
variables can be selected from the drop down menu at the top.  Middle
and right clicking in 3-d select the slice planes, and shift + middle
or right will extract 1-d lines through the data.  In 2-d, middle and
right clicking alone extract 1-d lines.

If \amrvis\ cannot find the {\tt Palette} file, then the plots will be
in grayscale.  To fix this, copy the {\tt amrvis.defaults} and {\tt
  Palette} files to your home directory and edit {\tt amrvis.defaults} so that
the {\tt palette} line points to the {\tt Palette} file, e.g.:
\begin{verbatim}
palette               /home/username/Palette
\end{verbatim}
